Autonomous Oceanographic Sampling Designs using Excursion Sets for Multivariate Gaussian random fields

### 2020-06-04 main_new.tex
updates

The AUVs considered here powered untethered platforms that operate at
$1$-$3$ m/s in the upper water column, where they are free to move in
six degrees of freedom (6 DOF). The in-water operation time capability
depends on survey speed, payload sensors and navigation; typically
this amounts to 8-48 hrs. AUVs typically use single-board computers
(SBCs), like the Raspberry Pi or a multicore GPU NVIDIA Jetson TX1
(quad-core 1.91 GHz 64-bit ARM machine, a 2-MB L2 shared cache, and 4
GB of 1600 MHz DRAM) for computation onboard.

>>>>

The AUVs considered here are powered untethered platforms, that
operate at $1$-$3$ m/s in the upper water column, where they are free
to move in six degrees of freedom (6 DOF). The in-water operation time
capability depends on survey speed, payload sensors and navigation;
typically this amounts to 8-48 hrs. AUVs typically use single-board
computers (SBCs), like the Raspberry Pi or a multicore GPU NVIDIA
Jetson TX1 (quad-core 1.91 GHz 64-bit ARM machine, a 2-MB L2 shared
cache, and 4 GB of 1600 MHz DRAM) for computation onboard.
